\projectprogress
\label{sec:progress}

\subsection{Pipeline Architecture}
The project is implemented as several Python modules that will all be combined
in a pipeline of five sequential stages. Stages~1--4 are complete and described
in this interim report; Stage~5 (the neural-network parameter optimization that
closes the loop on top of Stage~4) is planned for the second half of the
semester. Each stage is also exposed as a standalone module so that any subset
of the workflow can be re-executed in isolation. The current state of
completion of each stage is summarized in Table~\ref{tab:pipeline_status}.

\begin{table}[h]
	\centering
	\caption{Pipeline stages and current implementation status. Stage~5
	is detailed in Section~\ref{sec:future}.}
	\label{tab:pipeline_status}
	\renewcommand{\arraystretch}{1.2}
	\begin{tabular}{|c|p{6.5cm}|c|c|}
		\hline
		\textbf{Stage} & \textbf{Description} & \textbf{Framework} & \textbf{Status} \\ \hline
		1 & Random alloy configuration generation     & Python                       & Complete \\ \hline
		2 & MD elastic-property evaluation             & LAMMPS Python API            & Complete \\ \hline
		3 & DFT reference calculations                  & Quantum Espresso + ASE       & Complete \\ \hline
		4 & MEAM initialization and library merging     & Python                       & Complete \\ \hline
		5 & Neural-network surrogate optimization       & TensorFlow + LAMMPS          & Planned \\ \hline
	\end{tabular}
\end{table}

The data flow between stages is shown schematically in
Figure~\ref{fig:pipeline}. Stage~1 emits a JSON description of an alloy
configuration; Stage~2 simulates that configuration in LAMMPS and writes the
measured elastic moduli to a shared results database; Stage~3 produces DFT
reference values for every selected element and binary pair and stores them in
a reference-data database; Stage~4 reads both of these and emits a merged,
DFT-initialized pair of MEAM files. Stage~5 (planned) will consume those
files together with the LAMMPS-evaluated $(C_{11},C_{12})$ targets and
produce a final, refitted MEAM parameter set. A divergent composition-only
neural-network branch (dashed in Figure~\ref{fig:pipeline}) consumes the
Stage~2 elastic database as a sanity check but never feeds back into the
potential-fitting flow; it is described in Section~\ref{sec:comp_nn}.

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[
		stage/.style={rectangle, rounded corners, draw=black, fill=gray!10,
		              text width=2.6cm, minimum height=1.0cm, align=center, font=\small\bfseries},
		planned/.style={rectangle, rounded corners, draw=black, dashed, fill=gray!2,
		              text width=2.6cm, minimum height=1.0cm, align=center,
		              font=\small\bfseries\itshape},
		aux/.style={rectangle, rounded corners, draw=black, dashed, fill=blue!5,
		              text width=2.6cm, minimum height=1.0cm, align=center, font=\small\bfseries},
		arrow/.style={-Stealth, thick},
		plannedarrow/.style={-Stealth, thick, dashed},
		auxarrow/.style={-Stealth, thick, dashed},
		label/.style={font=\scriptsize, align=center},
		node distance=0.4cm and 0.4cm,
	]
		\node[stage] (s1) {Stage 1\\Configurations};
		\node[stage, right=of s1] (s2) {Stage 2\\MD: $E,\nu,C_{ij}$};
		\node[stage, right=of s2] (s3) {Stage 3\\DFT};
		\node[stage, right=of s3] (s4) {Stage 4\\MEAM init};
		\node[planned, right=of s4] (s5) {Stage 5\\NN optim\\(planned)};

		\draw[arrow] (s1) -- (s2);
		\draw[arrow] (s2) -- (s3);
		\draw[arrow] (s3) -- (s4);
		\draw[plannedarrow] (s4) -- (s5);

		\node[label, below=0.1cm of s1] {composition\\records};
		\node[label, below=0.1cm of s2] {elastic\\database};
		\node[label, below=0.1cm of s3] {DFT\\reference};
		\node[label, below=0.1cm of s4] {merged MEAM\\library};
		\node[label, below=0.1cm of s5] {refitted MEAM\\parameters};

		% Divergent ML sanity-check branch: consumes the elastic database
		% from Stage 2 but does not feed back into the main pipeline.
		\node[aux, above=0.9cm of s3] (ml) {ML branch\\(\S\ref{sec:comp_nn})};
		\draw[auxarrow] (s2.north) |- (ml.west);
		\node[label, right=0.1cm of ml] {sanity check\\$(E,\nu)$ predictor};
	\end{tikzpicture}
	\caption{Five-stage pipeline architecture: Stages~1--4 (solid arrows)
	are complete, Stage~5 (dashed, italicised) is planned. The dashed ML
	side-branch above Stage~3 is the composition surrogate of
	Section~\ref{sec:comp_nn}, which consumes the Stage~2 elastic
	database as a sanity check but never feeds back into the
	potential-fitting flow.}
	\label{fig:pipeline}
\end{figure}

\paragraph{What Stage~5 will do.}
Stage~5 will refit the cross-interaction terms of the merged MEAM library
emitted by Stage~4 to better reproduce the LAMMPS-evaluated elastic
targets. The plan, prototyped during this semester and detailed in
Section~\ref{sec:future}, has four steps:
\begin{enumerate}
	\item \textbf{Sample.} Draw $N$ perturbed parameter vectors
	      $\mathbf{p}_k = \mathbf{p}_0 \cdot (1+\boldsymbol{\eta}_k)$
	      around the Stage~4 baseline ($\eta_k\sim\mathcal{U}(-0.1,0.1)$
	      on each binary $(\texttt{Ec},\texttt{re},\texttt{alpha})$) and
	      run LAMMPS over every alloy in the elastic-property database
	      to obtain $(C_{11},C_{12})_k$ per composition. Samples whose
	      majority of compositions fail a $C_{11}>30$\,GPa physicality
	      check are rejected.
	\item \textbf{Train a surrogate.} Fit a feed-forward network
	      $\mathbf{p}\!\mapsto\!(C_{11,k},C_{12,k})_{k=1}^{N_\mathrm{entries}}$
	      with a Huber loss. Predicting the elastic constants directly
	      (rather than $\nu$, whose ratio form is ill-conditioned in
	      composition space) and using a robust loss are the two
	      lessons carried over from the composition surrogate of
	      Section~\ref{sec:comp_nn}.
	\item \textbf{Inverse optimization.} Find
	      $\hat{\mathbf{p}} = \arg\min_{\mathbf{p}} \lVert
	      f_\theta(\mathbf{p}) - \mathbf{y}^\star \rVert^2$ by Adam
	      descent on the normalised parameter vector, clipped to
	      $\pm 2.5\sigma$ around the training mean to keep the
	      optimization within the surrogate's domain of validity. A
	      physical-stability penalty
	      ($C_{11}+C_{12}>0$, $C_{11}\geq C_{12}$, $\nu<0.48$) will be
	      added to keep the inverse optimizer inside the
	      mechanically-stable region.
	\item \textbf{Validate.} Re-evaluate $\hat{\mathbf{p}}$ in LAMMPS,
	      derive $(E_\mathrm{opt},\nu_\mathrm{opt})$ analytically from
	      the predicted $(C_{11},C_{12})$, and compare against a
	      held-out set of named industrial alloys
	      (Al~2024, 2219, 5052, 7075 plus extensions) and at least two
	      non-aluminium alloys.
\end{enumerate}
The supporting infrastructure (parallel LAMMPS sampling, MPI
distribution, MEAM file I/O, $C_{11}/C_{12}$ persistence in
\texttt{results.json}) is already in place from the Stage~2 work
described in Section~\ref{sec:stage2}.

\newpage
