\subsection{External Validation Against Experimental Data}
\label{sec:validation}

The internal checks so far compare the surrogates against the project's own MD
output. The real test is experiment. Both the composition surrogate of
Section~\ref{sec:comp_nn} and the refit MEAM potential of
Section~\ref{sec:nnip} were run on 42 named alloys whose elements the merged
basis covers, and the predicted $(E,\nu)$ were compared against published
elastic data from ASM and MatWeb \citep{asmmatweb}. Mean absolute percentage
error (MAPE) is the figure of merit. Unphysical MEAM runs are excluded from
the MEAM column.

Table~\ref{tab:lit_family} breaks the comparison down by material family.
Inside the aluminium family, which is where the training data is densest, both
methods do well: the composition NN reaches $2.3\,\%$ MAPE on $E$ and the
refit MEAM $7.4\,\%$, with $\nu$ within $4$ to $5\,\%$ for both. Moving off the
aluminium domain, the two methods part ways. The composition NN degrades
gently, staying near $12\,\%$ on titanium and only failing badly on the
stainless alloys it has almost no training support for. The MEAM
potential degrades steeply: its error on titanium and stainless runs into the
hundreds of percent, which is the same instability seen on the held-out alloys
in Section~\ref{sec:nnip}, now measured against experiment.

\begin{table}[htbp]
	\centering
	\caption{Validation against ASM/MatWeb experimental elastic data, by
	material family ($N=42$ alloys). Values are MAPE in percent for the
	composition NN (ML) and the refit MEAM potential. Unphysical MEAM runs are
	excluded.}
	\label{tab:lit_family}
	\input{sections/_auto_literature_family}
\end{table}

Because aluminium is the design target, Table~\ref{tab:lit_al} drills into it
by AA series. The composition NN holds between $1.3$ and $3.8\,\%$ on $E$
across the 2xxx, 5xxx, 6xxx, and 7xxx series, and the refit MEAM stays under
$10\,\%$ across all four. For the 7xxx series, which includes the Al~7075 case
used as a running example, the NN lands at $2.8\,\%$ and the MEAM at $9.3\,\%$.
The takeaway is consistent with the rest of the report: within the
aluminium-rich region the pipeline produces a potential that matches
experiment to within a few percent, and the accuracy falls off only once the
composition leaves that region.

\begin{table}[htbp]
	\centering
	\caption{Aluminium validation drilled down by AA series ($N=33$ of the 42
	alloys). $\langle E_\mathrm{lit}\rangle$ is the mean experimental Young's
	modulus; the last two columns are $E$ MAPE for the composition NN (ML) and
	the refit MEAM potential.}
	\label{tab:lit_al}
	\input{sections/_auto_literature_al}
\end{table}

Table~\ref{tab:lit_al_detail} resolves the same comparison to individual alloy
grades. The composition surrogate is uniformly accurate on $E$: every grade in
the 2xxx, 5xxx, and 7xxx series lands within $3\,\%$ and the 6xxx grades within
$4\,\%$, with 2024 and 2017 the closest at $1.0$ and $1.2\,\%$. The refit MEAM
is more scattered, from $3.1\,\%$ on 6061 to $13.2\,\%$ on 5083. Its largest
errors fall on the higher-solute grades 5083, 2017, and 2219, where the Cu-,
Mn-, and Mg-bearing cross-terms are the least constrained by the Stage~2
sampling. The 6xxx series is the one place the physics-based potential matches
or beats the surrogate on $E$: 6061 comes in at $3.1\,\%$ for MEAM against
$3.8\,\%$ for the NN, because its dilute Al--Mg--Si chemistry sits closest to
the well-covered single-element aluminium reference.

The Poisson-ratio columns tell a complementary story. The surrogate holds
$\nu$ between $2.2$ and $5.4\,\%$ across every grade, while the MEAM error
swings from $0.1\,\%$ on 2017 to $7.2\,\%$ on 5083. Both models sit slightly
high on $\nu$, near $0.34$ to $0.35$ against the datasheet $0.33$. For
Al~7075, the running example, the surrogate stays within $2.6\,\%$ on $E$ and
$2.8\,\%$ on $\nu$, while the refit MEAM reaches $10.2$ and $5.1\,\%$, so the
data-driven route is the more reliable predictor for the design-target alloy.

One caveat is built into the table. The $N$ column counts datasheet entries,
which for a given grade are mostly different tempers of a single composition,
for example 2024-O, 2024-T3, and 2024-T4. Heat treatment changes the
microstructure but not the bulk composition, so both models return one
prediction per grade and the experimental $E$ varies by at most $1$\,GPa across
a grade's tempers. The comparison therefore measures how well composition alone
fixes the elastic constants, not how either model would track a temper or
precipitate state, which neither is built to capture.

\begin{table}[htbp]
	\centering
	\caption{Aluminium validation resolved to individual alloy grades. $N$ is
	the number of datasheet entries (tempers) per grade and
	$\langle E_\mathrm{lit}\rangle$ their mean experimental Young's modulus in
	GPa; the remaining columns are $E$ and $\nu$ MAPE in percent for the
	composition NN (ML) and the refit MEAM potential. Unphysical MEAM runs are
	excluded.}
	\label{tab:lit_al_detail}
	\input{sections/_auto_literature_al_detail}
\end{table}
