% =====================================================================
% Slide 13: Summary -- what was achieved vs what comes next
% Two parallel columns reusing the deck badge language:
%   filled darkred check badge = done; outlined number badge = next.
% =====================================================================

% --- local badge / row / header helpers (slide-specific) -------------
\newcommand{\achbadge}{\tikz[baseline=-0.6ex]{\node[fill=darkred, text=white,
  rounded corners=2.5pt, minimum size=1.7em, inner sep=0pt,
  font=\small\bfseries]{\checkmark};}}
\newcommand{\nextbadge}[1]{\tikz[baseline=-0.6ex]{\node[draw=darkred,
  line width=0.7pt, text=darkred, rounded corners=2.5pt, minimum size=1.7em,
  inner sep=0pt, font=\small\bfseries]{#1};}}
\newcommand{\achrow}[1]{\smallskip\par\noindent
  \achbadge\hspace{0.7em}\parbox[t]{0.80\columnwidth}{\small #1}\par}
\newcommand{\nextrow}[2]{\smallskip\par\noindent
  \nextbadge{#1}\hspace{0.7em}\parbox[t]{0.80\columnwidth}{\small #2}\par}

\begin{frame}{Summary \& Further Studies}
\begin{columns}[T]

% ---------- achieved ----------
\column{0.49\textwidth}
{\tikz{\node[fill=darkred, text=white, rounded corners=3pt, inner sep=5pt,
  font=\bfseries\scshape]{Achieved};}}
\par\vspace{0.4em}
\achrow{\textbf{Automated 12-element MEAM pipeline.} An end-to-end
  workflow that assembles a multi-element potential.}
\achrow{\textbf{Aluminium-alloy elastic prediction.}
  $E,\nu$ and $C_{11},C_{12}$ obtained from composition.}
\achrow{\textbf{DFT-seeded, NN-trained MEAM.} First-principles
  references refit through a neural surrogate.}

% ---------- next ----------
\column{0.49\textwidth}
{\tikz{\node[draw=darkred, line width=0.7pt, text=darkred,
  rounded corners=3pt, inner sep=5pt, font=\bfseries\scshape]{What comes next};}}
\par\vspace{0.4em}
\nextrow{1}{\textbf{More data coverage.} Wider sampling across the
  composition space and crystal structures.}
\nextrow{2}{\textbf{More NN training epochs.} Deeper surrogate
  convergence before each refit.}
\nextrow{3}{\textbf{Denser atomic-cell DFT.} Finer cells and
  supercell sampling for sharper references.}
\nextrow{4}{\textbf{Inverse design.} Specify a target $(E, \nu)$ and
  invert the composition surrogate to propose candidate alloys.}

\end{columns}

\vspace{0.7em}
\centering{\footnotesize The pipeline already runs end to end; what is left is
more data, longer training, denser DFT references, and running the predictor
in reverse.}
\end{frame}
